The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-08-12 presentations/presentation/presentation.tex
tried to make a figure for presentation
very good pictures for presentation
new intro figure, added intro slides

\documentclass{beamer}
\title{The Impact of Anthropogenic Forcing on ENSO Amplitude}
\author{Ben Goldman}
\date{\today}
\usepackage{natbib}
\usepackage{tikz}
\usetheme{metropolis}
\renewcommand{\bibsection}{}

@@

@@

  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
    \item Here we go...
    \item \cite{bjerknes1969atmospheric}
    \end{itemize}
    \column{0.5\textwidth}
    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{figures/example.jpg}
      \caption{This is a very nice figure}
      \label{fig:this}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}{El Niño}

@@

\begin{frame}{ENSO in the Future}
  Problem: What effect does global warming have on ENSO? Can we expect ENSO to become stronger, weaker, or neither?
\end{frame}

@@

\begin{frame}{References}
  \bibliographystyle{apalike}
  \bibliography{references.bib}
\end{frame}

>>>>

\documentclass{beamer}
\title{The Impact of Anthropogenic Forcing on ENSO Amplitude}
\author{Ben Goldman}
\date{\today}
\usepackage{natbib}
\usepackage{tikz}
\usetheme{metropolis}
\renewcommand{\bibsection}{}
\setbeamerfont{caption}{size=\tiny}

@@

\newcommand{\myfig}[3]{
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/#1}
    \caption{#2}
    \label{fig:#3}
  \end{figure}
}

@@

  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item The earth is getting warmer. \citep{pachauri2014climate}
    \item Climate varies on different scales.
    \item Long-term trends and short-term noise.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{intro_fig_3.pdf}{Global mean land air temperature in GISSTEMP 4 dataset. \citep{gistemp2019giss} and \citep{lenssen2019improvements}}{this}
  \end{columns}
\end{frame}

\begin{frame}{El Niño}
  \begin{figure}
    \begin{columns}
      \column{0.5\textwidth}
      \begin{itemize}
      \item Warming and cooling of the Pacific Ocean.
      \item Affects human societies through temperature and rainfall. \citep{ropelewski1987global}
      \item May be affected by climate change.
      \end{itemize}
      \caption{Comparison of SST anomaly between 1975 La Niña event and 1997 El Niño event in HadISST 1 dataset. \citep{rayner2003global}}
      \column{0.5\textwidth}
      \includegraphics[width = \textwidth]{figures/intro_fig.pdf}
    \end{columns}
  \end{figure}
\end{frame}

@@

\begin{frame}{ENSO in the Future}
\end{frame}

@@

\begin{frame}{References}
  \bibliographystyle{apalike}
  \fontsize{7pt}{7.2}\selectfont
  \bibliography{references.bib}
\end{frame}
